Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-02-19 Draft/acknowledgements.tex
Add acknowledgment
added acknowledgments

The authors would like to acknowledge the contribution of the COST Action CA16108 which initiated this work.
Moreover, this work was supported by sveral STSM Grant from the COST Action CA16108.

@@

AK acknowledge financial support by the Swiss National Science Foundation (SNF) under contract 200020-175595

>>>>

The authors would like to acknowledge the contribution of the COST Action CA16108 which initiated this work.
Moreover, this work was supported by several STSM Grant from the COST Action CA16108. Many authors acknowledge
hospitality from Nikhef, where part of this work was performed.

@@

MZ is supported
 by the Netherlands National Organisation for Scientific
 Research (NWO),
